Indirect Conflicts: An Exploration and Discussion of Tools, Process, and Developer Insight

### 2013-09-09 iced-2013/paper.tex

From the interviewed participants, 63\% of developers believe that a large contributing factor to the cause
of indirect conflicts comes from the changing of a software object's contract. One developer stated that ``design
by contract was invented to solve this problem and it does it quite well'', while another noted that software 
object contracts do solve the problem in theory, but that doesn't mean that problems don't occur in practice.
In light of object contracts, 73\% of interviewed developers gave examples of indirect conflicts they had experienced
which stemmed from not understanding the far reaching ramifications of a change being made to an object contract
towards the rest of the project. Of those 73\%, examples were broken down as follows. 21\% of examples had to do 
with the changing of legacy code, with one developer saying ``legacy code does not change because developers 
are afraid of the long range issues that may arise from that change''. 36\% of interviewed developers mentioned 
that indirect conflicts occur when an update to an external project, library, or service occurs and the resulting 
integration fails noting that major releases of libraries can be a large issue with one developer saying 
``their build never breaks, but it breaks ours''. Finally, 29\% of developers interviewed explained that changes to
databases are often a large source of indirect conflicts saying ``[schema changes] break stuff all over the place''.

@@

The results of~\ref{itm:rq5} show us how developers currently catch indirect conflicts. It appears that most indirect conflicts are currently
detected by using what some would call proper software practices. The use of unit and integration testing, and the use of nightly or weekly
project builds are the main contributing factors of such discovery. The words ``use case coverage'' were constantly being used by developers
when expressing how proper unit and integration tests should be written. Developers expressed that with proper use case coverage, most if
not all indirect conflicts should be caught. This leads us to believe that as long as the contract of a software structure is understood,
proper tests should be able to be written which will catch most if not all indirect conflicts. The problems occur when the contract is
not properly understood and use cases are not tested for or examined as explained in previous discussion. Once an object is not properly
tested, the negative consequences may not be caught until later in a project with the potential for more damage to be caused. Some languages
such as Eiffle and the Java Modeling Language enforce object contracts to be well understood through the ideas of pre and post conditions
of structures. Aside from testing
was the build process. Developers said that the build process is simply there to ensure a, at least, semi-functioning product. They use
the build process more to catch compile time errors witch prevent the product from being used. These types of build breaking indirect
conflicts do occur but for the most part developers posses tools capable to build their solutions in order to catch these problems before
the code change is added to the project. Therefore, unit and integration testing appears to be the largest factor in catching indirect conflicts.

@@

>>>>

From the interviewed participants, 63\% of developers believe that a large contributing factor to the cause
of indirect conflicts comes from the changing of a software object's contract. Object contracts are, in a sense,
what a software object guarantees, meaning how the input, output, or how any aspect of the object is garuntee
to work; made famous by Eiffle Software's~\footnote{http://www.eiffel.com/} ``Design by Contract''\textregistered. 
One developer stated that ``design
by contract was invented to solve this problem and it does it quite well'', while another noted that software 
object contracts do solve the problem in theory, but that doesn't mean that problems don't occur in practice.
In light of object contracts, 73\% of interviewed developers gave examples of indirect conflicts they had experienced
which stemmed from not understanding the far reaching ramifications of a change being made to an object contract
towards the rest of the project. Of those 73\%, examples were broken down as follows. 21\% of examples had to do 
with the changing of legacy code, with one developer saying ``legacy code does not change because developers 
are afraid of the long range issues that may arise from that change''. 36\% of interviewed developers mentioned 
that indirect conflicts occur when an update to an external project, library, or service occurs and the resulting 
integration fails noting that major releases of libraries can be a large issue with one developer saying 
``their build never breaks, but it breaks ours''. Finally, 29\% of developers interviewed explained that changes to
databases are often a large source of indirect conflicts saying ``[schema changes] break stuff all over the place''.

@@

The results of~\ref{itm:rq5} show us how developers currently catch indirect conflicts. It appears that most indirect conflicts are currently
detected by using what some would call proper software practices. The use of unit and integration testing, and the use of nightly or weekly
project builds are the main contributing factors of such discovery. The words ``use case coverage'' were constantly being used by developers
when expressing how proper unit and integration tests should be written. Developers expressed that with proper use case coverage, most if
not all indirect conflicts should be caught. This leads us to believe that as long as the contract of a software structure is understood,
proper tests should be able to be written which will catch most if not all indirect conflicts. The problems occur when the contract is
not properly understood and use cases are not tested for or examined as explained in previous discussion. Once an object is not properly
tested, the negative consequences may not be caught until later in a project with the potential for more damage to be caused. Some languages
such as Eiffle and the Java Modeling Language~\footnote{http://www.eecs.ucf.edu/~leavens/JML//index.shtml}
enforce object contracts to be well understood through the ideas of pre and post conditions of structures. Aside from testing
was the build process. Developers said that the build process is simply there to ensure a, at least, semi-functioning product. They use
the build process more to catch compile time errors witch prevent the product from being used. These types of build breaking indirect
conflicts do occur but for the most part developers posses tools capable to build their solutions in order to catch these problems before
the code change is added to the project. Therefore, unit and integration testing appears to be the largest factor in catching indirect conflicts.

@@

% insert here
